Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Formatting

In Figure \ref{oriented} port is red and starboard green. The sequence of zero/one variables for each skipper is shown on the left. Bottom right is the dfa, and top right is the final schedule produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. Three days cpu time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The schedule presented here is new, not appearing in the ISAF World Sailing Umpire's Manual.
\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the orientation process, stage 4. Top right is the actual oriented schedule. Below that is the dfa to satisfy criteria 5. On the left is the zero/one variables, a row representing a skippers sequence of competitors. An edge between variables corresponds to a matched pair, that must take different values. Bottom right is a sketch by one of the authors.}
\label{oriented} 
\end{figure}

>>>>

In Figure~\ref{oriented}, port is red and starboard green. The sequence of
zero/one variables for each skipper is shown on the left. Bottom right is the
DFA, and top right is the final schedule produced from stages 1 to 4. The
schedule has 6 boat changes and a maximum imbalance of 1. Three days CPU time
was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
schedule presented here is new, not appearing in the ISAF World Sailing
Umpire's Manual.

\begin{figure}[tb]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
\caption{A pictorial representation of the orientation process, stage 4. Top
right is the actual oriented schedule. Below that is the dfa to satisfy
criteria 5. On the left is the zero/one variables, a row representing a
skippers sequence of competitors. An edge between variables corresponds to a
matched pair, that must take different values. Bottom right is a sketch by one
of the authors.}
\label{oriented}
\end{figure}
